Ms 1

### 2018-01-09 ms1/ms1_display.Rmd
combined resp tables

```{r drug_trends}
est2pct = function(x) (x - 1)*100

drug_trends = read_tsv('tables/new/abx_models.tsv') %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', estimate, lower_ci, upper_ci))

drug_trends %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), function(x) format(x, digits=1, nsmall=1, scientific=FALSE)) %>%
  kable(caption='Drug trends: Percent change from 2011 to 2014')

drug_trends %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('n_pde', 'n_pde_approp', 'n_pde_inapprop', 'n_pde_nodx'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32.5), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

format_p = function(p) if_else(p<0.0001, '<.0001', format(round(p, 4), digits=4, nsmall=4))

combined_table = rxdx_table %>%
  mutate(cpkp=round(n_pdedx / bene * 1000, 1)) %>%
  filter(year %in% c(2011, 2014)) %>%
  select(antibiotic, dx_cat, year, cpkp) %>%
  spread(year, cpkp) %>%
  right_join(rxdx_models, by=c('antibiotic', 'dx_cat')) %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', estimate, lower_ci, upper_ci)) %>%
  mutate(d=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change2=sprintf('%.1f ± %.1f', estimate, d)) %>%
  mutate(p.value=format_p(p_value)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, change2, p.value) %>%
  arrange(dx_cat, antibiotic)
```

@@

rxdx_kable(c('azithromycin', 'levofloxacin', 'amoxclav'),
           c('pneumonia', 'sinusitis', 'uri', 'bronchitis'))
```

@@

## Other respiratory

```{r other_respiratory}
rxdx_kable(c('azithromycin', 'levofloxacin', 'amoxclav'),
           c('pharyngitis', 'asthma', 'other_resp'))
```

>>>>

```{r abx_trends}
est2pct = function(x) (x - 1)*100
format_p = function(p) if_else(p<0.0001, '<.0001', format(round(p, 4), digits=4, nsmall=4))

ceiling_at = function(x, n) {
  mult = 10 ** n
  x %>% { . * mult } %>% ceiling %>% { . / mult }
}

format_model = function(df) {
  df %>%
    mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
    mutate(pm=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
    mutate(change=sprintf('%.1f ± %.1f', estimate, ceiling_at(pm, 1))) %>%
    mutate(p.value=format_p(p_value))
}

abx_trends = read_tsv('tables/new/abx_models.tsv') %>%
  format_model()

abx_trends %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), function(x) format(x, digits=1, nsmall=1, scientific=FALSE)) %>%
  kable(caption='Drug trends: Percent change from 2011 to 2014')

abx_trends %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('n_pde', 'n_pde_approp', 'n_pde_inapprop', 'n_pde_nodx'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32.5), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

combined_table = rxdx_table %>%
  mutate(cpkp=round(n_pdedx / bene * 1000, 1)) %>%
  filter(year %in% c(2011, 2014)) %>%
  select(antibiotic, dx_cat, year, cpkp) %>%
  spread(year, cpkp) %>%
  right_join(rxdx_models, by=c('antibiotic', 'dx_cat')) %>%
  format_model() %>%
  select(dx_cat, antibiotic, `2011`, `2014`, change, p.value) %>%
  arrange(dx_cat, antibiotic)
```

@@

rxdx_kable(c('azithromycin', 'levofloxacin', 'amoxclav'),
           c('pneumonia', 'sinusitis', 'uri', 'bronchitis', 'other_resp', 'asthma'))
```

@@
